Sulfur Dioxide at Water's Surface

### 2010-12-17 Methods.tex
Fleshing out with new sections
New image for the spherical angle definition, fleshed out the section describing the angles theta and phi for orientation analysis. Added bibliography for citations
Explaining the MD methods for SMD and pre-quilibrated systems

\subsection{Molecular Dynamics Simulations}

\subsection{Steered Molecular Dynamics Trajectories}

>>>>

Molecular dynamics simulations were performed using the Amber 11 software suite.\cite{Case2010} In this study we incorporate polarizable models for the \wat~and \suldiox~molecules. Fully polarizable models have been used previously in studies on interfacial systems because they are known to more accurately reproduce interfacial structure and free energy profiles.\cite{Wick2007,Rivera2006,Dang1998} The \wat~model used is the POL3 model,\cite{Caldwell1995} and for \suldiox we used the model of Dang, et al. that places a single polarizable center on the sulfur atom.\cite{Baer2010}

All simulations began with an equilibrated box of 900 \wat~molecules, with sides of length 30\angs. The simulations all employed periodic boundaries to create an ``infinite-slab'' geometry for the water phase. One set of simulations involved adding a single \suldiox~to the center of the water box and then allowing the system to equilibrate over 1 ns of simulation. The ensuing simulations are herein referred to as the ``surface equilibrated'' simulations.

A second set of simulations involved preparing a water slab as explained above. A single \suldiox~was then introduced 20\angs above the slab, with the sulfur atom tethered to its initial position. The system was evolved for 1 ns, taking coordinate snapshots every 20 ps to create 50 starting points for further simulations. Steered molecular dynamics (SMD) were then performed to guide the \suldiox~down towards a tethered water 15\angs under the water slab surface by applying a small steering force.\cite{Isralewitz2001} The \suldiox~thus passed through the continuum of environments from gas phase to hydrate complex interaction, water surface adsorption, and absorption into the bulk of the neat-\wat~slab.

The third set of simulations were performed similarly to the neat-\wat~SMD simulations, but the water slab and gas phase above it were first loaded with \suldiox. The water slab was loaded with 22 \suldiox molecules, which represent a saturation level coinciding with the Henry's law constant for \suldiox~in \wat. The gas phase was populated with 50 \suldiox~molecules representing approx. 50 atm of \suldiox~pressure.

\subsection{Steered Molecular Dynamics}
